### 2014-09-03 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to HRR description

To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used. Based on these sources of information, the FDS model includes two source fires: an initial couch fire in the basement near the rear side of the structure, and a secondary flashover fire that spanned the entire basement floor area. The basement primarily contained upholstered polyurethane furniture fuel items. The HRR of the initial couch fire is based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.

@@

% The first 300~s of the HRR in the simulation follow the mattress HRR. After 300~s, the specified fire size is 20~MW.

@@

\begin{lstlisting}
&SURF ID='BURNER', HRRPUA=0.25, COLOR='RED', RAMP_Q='Fire_Ramp' /
&VENT XB=4.2, 6.2, 15.2, 17.2, -2.8, -2.8, SURF_ID='BURNER' /

&SURF ID='FLASHOVER_BURNER', HRRPUA=270.563, COLOR='RED' /
&VENT XB=0.0, 8.4, 8.5, 15.1, -2.8, -2.8, SURF_ID='FLASHOVER_BURNER', DEVC_ID='TIMER_FLASHOVER' /
&DEVC ID='TIMER_FLASHOVER', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.FALSE., SETPOINT=300 /
\end{lstlisting}
Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes located at a specific area.

>>>>

To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used. Based on these sources of information, the FDS model includes two source fires: an initial couch fire in the basement near the rear side of the structure, and a secondary flashover fire that involved the entire basement floor area. The basement primarily contained upholstered polyurethane furniture fuel items. The HRR of the initial couch fire is based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.

@@

The HRR was prescribed in FDS as follows. From 0~s to 300~s, the HRR in the simulation followed the experimentally measured mattress HRR. At 300~s, the HRR was approximately 3~MW. From 300~s to 342~s (the time at which the first basement window failed), the HRR increased linearly from 3~MW to 20~MW. From 342~s to 540~s, the HRR was 15~MW. Note that the prescribed HRR can be different than the simulated HRR calculated by FDS based on the amount of available fuel, oxygen, and ventilation. A comparison of the prescribed HRR and the simulated HRR is discussed in Section~\ref{sec:HRR}.

@@

\begin{lstlisting}
&SURF ID='BURNER', HRRPUA=0.25, COLOR='RED', RAMP_Q='Mattress_Ramp' /
&VENT XB=4.2, 6.2, 15.2, 17.2, -2.8, -2.8, SURF_ID='BURNER', DEVC_ID='TIMER_INITIAL_BURNER_OFF' /
&DEVC ID='TIMER_INITIAL_BURNER_OFF', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.TRUE., SETPOINT=300 /

&SURF ID='FLASHOVER_BURNER', HRRPUA=0.018255, COLOR='RED', RAMP_Q='Flashover_Ramp' /
&VENT XB=0.1, 8.4, 8.5, 15.1, -2.8, -2.8, SURF_ID='FLASHOVER_BURNER' /
\end{lstlisting}
Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes located at a specific area.
